---
title: "p8105_hw3_jsg2145"
author: "Jared Garfinkel"
date: "10/9/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r, cache = TRUE}
library(p8105.datasets)
data("instacart")
data("brfss_smart2010")
```

The "instacart" dataset is `r nrow(instacart)` rows by `r ncol(instacart)` columns. 

There are a few variables that appear to be key to telling us what the dataset is. 

The variable "product_name" is an item that was placed in a cart. Order have an "order_id" number.

Each item in a cart has an "add_to_cart_order", for instance, in the head of the data, "order_id" 1

had 8 items added, 1 through 8 and "add_to_cart_order" gives the order in which the 

items were added.  There are columns that tell the time of day of the order, the days 

since the prior order, and whether a specific item was reordered or not. There are 

also details about where the item is found (aisle, department)

```{r}
aisle_dat <- instacart %>% 
  group_by(aisle) %>%
  summarize(
    count = n()) %>% 
  arrange(desc(count))
```

## Problem 1

There are `r nrow(aisle_dat)` aisles, and `r pull(top_n(aisle_dat, 1, count), aisle)` was the aisle the most items were ordered from.

```{r, fig.width = 10}
instacart %>% 
  group_by(aisle) %>% 
  count() %>% 
  filter(
    n > 10000
  ) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_col() +
  labs(xlab = "Count",
       ylab = "Aisle")

```

```{r}
instacart %>% 
  filter(
    aisle == c("baking ingredients", 
               "dog food care", 
               "packaged vegetables fruits")
    ) %>% 
  mutate(
    aisle = 
      recode(aisle,
             "baking ingredients" = "Baking Ingredients",
             "dog food care" = "Dog Food Care",
             "packaged vegetables fruits" = "Packaged Vegetables Fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(
    count =  n()
  ) %>% 
  top_n(., 3, count) %>% 
  arrange(desc(count), .by_group = TRUE) %>% 
  rename(Aisle = aisle,
         "Product Name" = product_name,
         Count = count) %>% 
  knitr::kable()
```

```{r}
instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(
    mean_hr = round(mean(order_hour_of_day), digits = 1)
  ) %>% 
  mutate(
    order_dow = factor(order_dow, 
                       labels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))) %>%
  rename("Product Name" = product_name) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hr
  ) %>% 
  knitr::kable()
  
  
```

## Problem 2

```{r}
brfss_smart2010 <- brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>%
  mutate(
    response = factor(response, 
                      labels  = c("Poor", "Fair", "Good", "Very good", "Excellent")),
    state = match(locationabbr, state.abb),
    state = state.name[state],
    state = replace_na(state, "District of Columbia")
  ) %>% 
  arrange(response)
```

```{r}
brfss_smart2010 %>% 
  filter(year == 2002) %>% 
  select(state) %>% 
  group_by(state) %>% 
  count() %>% 
  filter(n > 6) %>% 
  rename(State = state,
         Locations = n) %>% 
  knitr::kable()
```
```{r}
brfss_smart2010 %>% 
  filter(year == 2010) %>% 
  select(state, locationdesc) %>% 
  group_by(state) %>% 
  count() %>% 
  filter(n > 6) %>% 
  rename(State = state,
         Locations = n) %>% 
  knitr::kable()
```

```{r}
df <- brfss_smart2010 %>% 
  filter(response == "Excellent") %>% 
  group_by(year, state) %>% 
  summarize(
    mean_dat = mean(data_value)
  ) %>% 
  select(year, state, mean_dat)
```

```{r, fig.width = 10, fig.height = 6}
df %>% 
  ggplot(aes(x = year, y = mean_dat, group = state, color = state)) +
  geom_line() +
  theme(legend.position = "bottom") +
  viridis::scale_color_viridis(
    name = "state",
    discrete = TRUE)
```

```{r}
brfss_smart2010 %>% 
  filter(state == "New York",
         year == c(2006, 2010)) %>% 
  ggplot(aes(x = response, y = data_value)) +
  geom_boxplot() +
  labs(x = "Response",
       y = "Data Value") +
  facet_grid(~year)

```

## Problem 3

```{r}
accel_dat <- read_csv("./data/accel_data.csv") %>% 
  pivot_longer(
    cols = activity.1:activity.1440,
    names_to = "minute",
    values_to = "activity") %>% 
  group_by(day) %>% 
  mutate(
    weekday = ifelse(day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), "Weekday", "Weekend")
  )
```

There are `r nrow(accel_dat)` rows and `r ncol(accel_dat)` columns in this dataset. There is a minute

variable for each minute of a day, a weekday variable for whether the day of the week is a weekend or 

a weekday, a week variable for each of the five weeks of observations, and a variable, "day_id" for 

each day in the study. The final variable measures the activity of the subject at each interval.

```{r, echo = FALSE}
accel_dat %>% 
  aggregate(activity ~ day_id, data = ., sum) %>% 
  ggplot(aes(x = day_id, y = activity)) +
  geom_point() + geom_smooth(se = FALSE)
```

```{r}
accel_dat %>% 
  aggregate(activity ~ day_id, data = ., sum) %>% 
  knitr::kable()
```

```{r, fig.width = 8}
accel_dat %>% 
  group_by(day_id, weekday) %>%
  mutate(
    day_act = cumsum(activity)
  ) %>% 
  summarize(
    day_act = last(day_act)
  ) %>% 
  rename(Weekday = weekday) %>% 
  ggplot(aes(x = day_id, y = day_act, color = Weekday)) +
  geom_point() + 
  geom_smooth(se = FALSE) +
  labs(
    x = "Day of Study (1-35)",
    y = "Total Activity"
  ) +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits = 0:36)
  
```

```{r}
accel_dat %>% 
  select(weekday, day_id, day)
```

